---
title: "Estimation of Cpm* under PMITICS"
author: "Dr. Riyadh Al-Mosawi and Prof. Sanku Dey"
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, eval = FALSE, warning = FALSE,
  message = FALSE, collapse = TRUE, comment = "#>"
)
```

# Overview

This repository contains the R and Rcpp code for the paper
**“Estimation of $\mathcal{C}_{pm}^{*}$ under Progressive Multiple-Interval
Type-I Censoring: Bayesian and Classical Approaches with a Log-Logistic
Distribution.”**

The code computes MLEs, MPSEs, bootstrap confidence intervals, Lindley and
Tierney--Kadane Bayesian approximations, and MCMC estimates with HPD credible
intervals under SEL and LINEX losses.

# Files

* `UserFunLogLogistPMITICS_cpp.cpp`: main Rcpp functions.
* `Simulation.R`: Monte Carlo simulation code.
* `README.Rmd`: source of the GitHub documentation.

# Required packages

```{r packages}
packages <- c(
  "Rcpp", "RcppArmadillo", "RcppEigen", "RcppNumerical",
  "RcppProgress", "roptim", "pracma", "coda", "progress"
)

missing <- packages[
  !vapply(packages, requireNamespace, logical(1), quietly = TRUE)
]

if (length(missing) > 0L) {
  install.packages(missing, repos = "https://cloud.r-project.org")
}
```

Compile the C++ functions:

```{r compile}
Rcpp::sourceCpp("UserFunLogLogistPMITICS_cpp.cpp")
```

# Main functions

| Function | Description |
|:---------|:------------|
| `cdf_cpp()`, `pdf_cpp()`, `sur_cpp()`, `qnt_cpp()` | Log-logistic distribution functions |
| `Cpm_star_fun_cpp()` | Computes $\mathcal{C}_{pm}^{*}$ |
| `simulate_PMITICS_cpp()` | Generates a PMITICS sample |
| `loglik_cpp()`, `logmps_cpp()` | Log-likelihood and log-product-spacing functions |
| `Estim_profile_cpp()` | Computes MLE or MPSE, ESEs, and ACIs |
| `Boot_fun_cpp()` | Computes bootstrap confidence intervals |
| `Lindley_GEL_cpp()`, `Lindley_LINEX_cpp()` | Lindley approximations |
| `TK_GEL_cpp()`, `TK_LINEX_cpp()` | Tierney--Kadane approximations |
| `MCMC_cpp()` | MCMC estimates and HPD credible intervals |

Use `type = "LK"` for likelihood-based inference and `type = "PS"` for
product-spacing-based inference.

# Simulation settings

```{r settings}
index_set <- 8
index_scheme <- 3

Sim_no <- 500
B <- 1000

MC_size <- 20500
MC_burn <- 500

c_val1 <- -1.5
c_val2 <-  1.5
```

For a quick test, reduce `Sim_no`, `B`, and `MC_size`. Reduced settings
should not be used to reproduce the paper's numerical results.

# Run the simulation

Place the R and C++ files in the same folder. Remove or modify any
machine-specific `setwd()` command, and then run:

```{r run}
source("Simulation.R")
```

The program estimates $\beta$, $\gamma$, and $\mathcal{C}_{pm}^{*}$. The
result arrays contain the estimate, bias, squared error, estimated standard
error, interval limits, interval length, and coverage indicator. A checkpoint
is saved after every 50 successful replications.

# Create the GitHub README

```{r render}
rmarkdown::render("README.Rmd", output_format = "github_document")
```

Upload `README.Rmd` and the generated `README.md` to GitHub.
